10th International Satisfiability Modulo Theories Competition (SMT-COMP 2015): Rules and Procedures

### 2015-06-20 rules/rules15.tex
Grammar.

\header{Benchmark selection.}
%
The benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Retire inappropriate benchmarks.} The competition
  organizers may remove from the eligibility pool certain benchmarks
  that are inappropriate\footnote{In 2015, this (again) includes all
    benchmarks that use bit-vector division or remainder, because of
    an unresolved discussion about the semantics of division by zero.}
  or uninteresting for competition, or cut the size of certain
  benchmark families to avoid their over-representation.
\item \emph{Eliminate benchmarks whose status is unknown.} Any
  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
  is removed.  There is a significant number of benchmarks with {\tt
    unknown} status in the library; these are certainly interesting
  and are a challenge to solve, but they are not used in the
  competition.\footnote{Incremental benchmarks may contain multiple
    \akey{check-sat} commands, each with its own status.  Incremental
    benchmarks that contain (some) \akey{check-sat} commands with {\tt
      unknown} status may still contain a prefix of commands where the
    status is known for all \akey{check-sat} commands in the prefix.
    This prefix is eligible for the application track.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

>>>>

\header{Benchmark selection.}
%
The benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Retire inappropriate benchmarks.} The competition
  organizers may remove from the eligibility pool certain benchmarks
  that are inappropriate\footnote{In 2015, this (again) includes all
    benchmarks that use bit-vector division or remainder, because of
    an unresolved discussion about the semantics of division by zero.}
  or uninteresting for competition, or cut the size of certain
  benchmark families to avoid their over-representation.
\item \emph{Eliminate benchmarks whose status is unknown.} Any
  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
  is removed.  There are a significant number of benchmarks with {\tt
    unknown} status in the library; these are certainly interesting
  and are a challenge to solve, but they are not used in the
  competition.\footnote{Incremental benchmarks may contain multiple
    \akey{check-sat} commands, each with its own status.  Incremental
    benchmarks that contain (some) \akey{check-sat} commands with {\tt
      unknown} status may still contain a prefix of commands where the
    status is known for all \akey{check-sat} commands in the prefix.
    This prefix is eligible for the application track.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.
